Incentivizing Exploration by Heterogeneous Users

### 2018-02-17 introduction.tex

To effect an outcome close to societally optimal,
it is necessary to provide exploration incentives to the individual users.
This was noted in two recent lines of work:
\citet{kremer2014implementing}
and \citet{mansour2015bayesian,mansour2016bayesian}
assume that the site (also called the \emph{principal}) has an
informational advantage in being the only one to observe the results
of past arm pulls.
(Such an assumption applies, for instance, to route recommendations in
driving.)
The principal can exploit this advantage and make recommendations to
the individual agents which it is in their best interest to follow.
\citet{frazier2014incentivizing} and 
\citet{han2015incentivizing} instead assume that the results of all
past arm pulls are publicly observable
(such as reviews on an online retail site).
They instead allow payments which the principal can offer to users as
a reward for pulling particular arms.
We follow the model of \citet{frazier2014incentivizing} and
\citet{han2015incentivizing} 
and consider a multi-armed bandit model in which the principal can
offer payments to the users for pulling particular arms.

@@

\dkcomment{Rearranging the next two paragraphs a bit.}
Heterogeneity presents both a challenge and an opportunity.
On the one hand, \dkedit{unobserved heterogeneity} hides critical
information about an agent's preferences from the principal.
On the other hand, heterogeneity also presents an opportunity, through the
possibility of ``free exploration.''
Even when left unincentivized, agents will
play a variety of arms, revealing information about these arms' attributes.
This stands in sharp contrast to the case of homogeneous preferences, where 
unincentivized agents will herd onto a single apparently best arm, and providing
essentially any exploration at all requires incentives.

In order to take advantage of unobserved heterogeneity, the principal
has to give up some control, allowing the agent to reveal his
preferences through action, rather than obscuring them with incentives.
However, the principal cannot give up control completely,
and must use incentives to force agents to explore against their
preferences, for the greater good.

With these challenges and opportunities in mind, our goal is to understand the
impact of user heterogeneity on our ability to achieve high social utility with
low incentive payments, and on the best approaches for doing so.
We wish to understand whether incentivizing exploration with
heterogeneous preferences  is ``harder'' or ``easier'' than with
homogeneous ones,
and to understand how exploration strategies that do well in the
heterogeneous preference setting differ from those in the homogeneous one.

Toward that end, we model our setting as follows.
(We describe our model at a high level here,
with formal definitions given in Section~\ref{sec:prob}.)
Arms and users (or \emph{agents}) are characterized by payoff-relevant
\emph{attribute} (or \emph{feature}) vectors.
\dkedit{Arms' attributes are a priori unknown, and
  agents' attributes are drawn from a known distribution.}
An agent's reward from pulling an arm is the inner product of their
vectors (plus noise).
When an arm is pulled, a noisy version of its attribute vector is
observed by everyone.
Agents are myopic and will pull the arm whose expected attribute
vector (based on past noisy observations) maximizes their reward.
The principal can incentivize agents to pull particular arms by
offering rewards for the specific arm.
The principal's goal is to keep the cumulative regret across all
agents small, while incurring only small total payments.
Our main theorem can be stated informally as follows:

>>>>

To effect an outcome close to societally optimal,
it is necessary to provide exploration incentives to the individual users.
This was noted in two recent lines of work:
\citet{kremer2014implementing}
and \citet{mansour2015bayesian,mansour2016bayesian}
assume that the site (also called the \emph{principal}) has an
informational advantage in being the only one to observe the results
of past arm pulls.
(Such an assumption applies, for instance, to route recommendations in
driving.)
The principal can exploit her%
\footnote{We use male pronouns to refer to users and female pronouns
  to refer to the principal.}
advantage and make recommendations to the individual agents which it
is in their best interest to follow.
\citet{frazier2014incentivizing} and 
\citet{han2015incentivizing} instead assume that the results of all
past arm pulls are publicly observable
(such as reviews on an online retail site).
They instead allow payments which the principal can offer to users as
a reward for pulling particular arms.
We follow the model of \citet{frazier2014incentivizing} and
\citet{han2015incentivizing} 
and consider a multi-armed bandit model in which the principal can
offer payments to the users for pulling particular arms.

@@

\dkcomment{Rearranging the next two paragraphs a bit.}
Heterogeneity presents both a challenge and an opportunity.
On the one hand, \dkedit{unobserved heterogeneity} hides critical
information about an agent's preferences from the principal.
On the other hand, heterogeneity also presents her an opportunity,
through the possibility of ``free exploration.''
Even when left unincentivized, agents will
play a variety of arms, revealing information about these arms' attributes.
This stands in sharp contrast to the case of homogeneous preferences,
where unincentivized agents will herd onto a single apparently best arm;
thus, effecting essentially any exploration at all requires incentives.

In order to take advantage of unobserved heterogeneity,
the principal has to give up some control, allowing the agent to
reveal his preferences through action, rather than obscuring them with
incentives.
However, she cannot give up control completely,
and must use incentives to force agents to explore against their
preferences, for the greater good.

With these challenges and opportunities in mind, our goal is to understand the
impact of user heterogeneity on the principal's ability to achieve
high social utility with low incentive payments,
and on the best approaches for doing so.
We wish to understand whether incentivizing exploration with
heterogeneous preferences  is ``harder'' or ``easier'' than with
homogeneous ones,
and to understand how exploration strategies that do well in the
heterogeneous preference setting differ from those in the homogeneous one.

Toward that end, we model our setting as follows.
(We describe our model at a high level here,
with formal definitions given in Section~\ref{sec:prob}.)
Arms and users (or \emph{agents}) are characterized by payoff-relevant
\emph{attribute} (or \emph{feature}) vectors.
\dkedit{Arms' attributes are a priori unknown, and
  agents' attributes are drawn from a known distribution.}
An agent's reward from pulling an arm is the inner product of his
vector with the arm's vector (plus noise).
When an arm is pulled, a noisy version of its attribute vector is
observed by everyone.
Agents are myopic and will pull the arm whose expected attribute
vector (based on past noisy observations) maximizes their reward.
The principal can incentivize agents to pull particular arms by
offering rewards for the specific arm.
The principal's goal is to keep the cumulative regret across all
agents small, while incurring only small total payments.
Our main theorem can be stated informally as follows:
